Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-10 documentation/paper.tex
Explained table

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), and still without $WallCut(D)$, $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with this configuration was 91\% (although with a high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

>>>>

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), and still without $WallCut(D)$, $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with this configuration was 91\% (although with a relatively high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

This chart shows that simple network architectures seem to produce better accuracy, likely due to reduced overfitting. Larger kernel sizes, more filters, and more layers make performance generally worse, while higher L2 regularization does the opposite. Dropout seems to have a weak correlation, possibly reducing accuracy slightly.
